---
title: "Downloading data from {themeparkr}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Downloading data from {themeparkr}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(themeparkr)
library(dplyr)
library(purrr)
library(tidyr)
```

Get static park data filtered for Walt Disney World.    
Filter for "attractions" that are actual rides.    
```{r}
wdw_park_tbl = tpr_destinations() %>%
  filter(parks_name %in% c("Magic Kingdom Park", "EPCOT",
                           "Disney's Hollywood Studios",
                           "Disney's Animal Kingdom Theme Park"))
wdw_children_tbl = wdw_park_tbl$parks_id %>%
  map_dfr(.f = tpr_entity_children)

wdw_attraction_tbl = wdw_children_tbl %>%
  filter(entityType == "ATTRACTION")

wdw_attraction_detail_tbl = wdw_attraction_tbl$id %>%
  map_dfr(.f = tpr_entity)

wdw_rides_detail_tbl = wdw_attraction_detail_tbl %>%
  filter(attractionType == "RIDE")

wdw_rides_detail_tbl
```

Extract latitude and longitude from location field.    
Pivot to 2 new colums.   
```{r}
rides_w_coord = wdw_rides_detail_tbl %>% 
  unnest_longer(location,values_to = "location",indices_to = "location_id") %>%
  filter(location_id %in% c("latitude","longitude")) %>%
  mutate(location = as.numeric(location)) %>%
  pivot_wider(names_from = "location_id", values_from = "location")

rides_w_coord
```

Get live wait time data.   
This is separate in case we want to make this "on-demand" to the user.    
Anchor to the static parks above as that would not change.   .
```{r}
live_rides = rides_w_coord %>%
  left_join(
    rides_w_coord$id %>% map_dfr(.f = ~tpr_entity_live(.x)),
    by = "id"
  )

live_rides_open = live_rides %>%
  filter(status %in% c("OPERATING", "DOWN"))

live_rides_open
```

more data wrangling for wait times
show park name, ride name, wait time, last updated
```{r}
c = b %>%
  mutate(
    wait_time = queue %>%
      map_int(pluck, "STANDBY", "waitTime", .default = NA_integer_),
    ll_time = queue %>%
      map_chr(pluck, "RETURN_TIME", "returnStart", .default = NA_character_)
  ) %>%
  left_join(p, by = c("parkId" = "parks_id")) %>%
  select(parks_name, id, name, status, ll_time,wait_time,lastUpdated) %>%
  mutate(
    across(
      .cols = all_of(c("ll_time", "lastUpdated")),
      .fns = lubridate::ymd_hms
    )
  ) %>%
  arrange(desc(wait_time)) %>% 
  mutate(
    status_cols = case_match(status,
                             "OPERATING" ~ "blue",
                             "DOWN" ~ "orange"
    )
  )

library(reactable)
c %>%
  mutate(
    status_cols = case_match(status,
                             "OPERATING" ~ "blue",
                             "DOWN" ~ "orange"
    )
  ) %>%
  reactable(
    theme = fivethirtyeight(centered = TRUE, header_font_size = 11),
    pagination = TRUE,
    showSortIcon = FALSE,
    highlight = TRUE,
    compact = TRUE,
    selection = "single",
    onClick = "select",
    defaultSelected = 1,
    columns = list(
      id = colDef(show = FALSE),
      parks_name = colDef(show = FALSE),
      name = colDef(
        align = "left",
        cell = merge_column(., "parks_name", merged_position = "below"),
      ),
      status = colDef(
        maxWidth = 150,
        name = "Status",
        align = "center",
        cell = pill_buttons(., color_ref = "status_cols", opacity = 0.7),
      ),
      status_cols = colDef(show = FALSE),
      wait_time = colDef(
        maxWidth = 50,
        name = "Wait (min.)",
        align = "center"
      ),
      ll_time = colDef(
        name = "Next LL Time"
      ),
      lastUpdated = colDef(
        name = "Last Updated"
        )
  )
)
```


Leaflet map of locations
dot markers of locations
orange for 'down' rides
blue to operating
```{r}
library(leaflet)
a = get_static_data()
b = get_live_data(a)

leaflet(data = b) %>%
  addTiles() %>%
  addCircleMarkers(
    lat = ~latitude,
    lng = ~longitude,
    color = ~ifelse(status == "OPERATING", "blue", "orange"),
    stroke = TRUE, fillOpacity = 0.75
  )
```

display data with reactable
```{r}

```

